Optimizer
========================================================

This is a total rewrite of the optimizer code.  Each criterion will have a optimal (0) and a min and max.  Crossing 95% min or max should be an order of magnitude effect, i.e. 10.  Crossing min or max is a two order of magnitude effect, i.e. 100.  Within the range we want a relatively smooth function that quickly accelerates (beyond 10% deviance from optimal to 1).  A curve would be awesome, but for now I'll settle for lines.
```{r optimBasic}
# F(t) = A(1 - t)^2 + 2B(1 - t)t + Ct^2
# y = d(1 - t)^2 + 2e(1 - t)t + ft^2
# 
# blah <- splinefun(c(-4,-2,0,1,3),c(10,1,0,1,10))
# plot(seq(-10,10,by=.01),blah(seq(-10,10,by=.01)),type="l")
# 
# monotonic <- function(x) {
#   x[1:(length(x)-1)] <- ifelse(x[1:(length(x)-1)] < x[2:(length(x)-1)],
# }
# splineFUN <- function(val, optim, mini, maxi) {
#   val <- val-optim #is the amount val is in excess of optimum.
#   mini <- mini-optim
#   maxi <- maxi-optim
#   lower <- sin(seq(pi/2,0,length.out=10))
#   upper <- sin(seq(0,pi/2,length.out=10))
#   splineFn <- splinefun(c(lower*mini,optim,maxi*upper),c(100,10:2,0,2:10,100))
#   res <- splineFn(val)
#   res <- ifelse(res > maxi,100,res)
#   res <- ifelse(res < mini,100,res)
#   res[res < 0] <- 0
#   res[res > 100] <- 100
#   return(res)
# }
rweight <- function(val,optimV,minV,maxV) {
  dev <- abs(val-optimV)
  functionalLowerRange <- optimV-minV
  functionalUpperRange <- maxV-optimV
  prop <- ifelse(sign(val-optim)==-1, dev/functionalLowerRange, dev/functionalUpperRange)
  res <- ifelse((prop > .90) & (prop < 1),abs(prop-1)*999+1,prop)
  res <- ifelse((val < minV) |(val > maxV),999+((1+(dev/optim))^2),res)
  return(res)
}

```

## Load USDA
```{r}
library(repsych)
glibrary(data.table,doBy,reshape2,knitr,parallel)

purl("Nutrient Research.Rmd")
source("Nutrient Research.R")
load("./sr25/USDA.Rda")
mgrepl <- function(pattern,x) {
  apply(sapply(pattern,grepl,x=x),1,any)
}
foodWithData <- merge(targetFood,NUT_DATA,by="NDB_No")
longres <- merge(foodWithData,NUTR_DEF,by="Nutr_No")
longres[NutrDesc=="Energy",NutrDesc:=Units]
USDAwide <- as.data.table(dcast(longres,Long_Desc+NDB_No+Refuse~NutrDesc+Units,value.var="Nutr_Val"))



#USDA database doesn't track cost

#USDAwide <- merge(USDAwide,WEIGHT,by="NDB_No")
#dput(USDAwide[1,])
#USDAwide[Long_Desc=="Butter, salted",]
#template <- lapply(USDAwide[1,],unfactor)
#dput(template,file="clipboard")

#
setnames(USDAwide,names(USDAwide),gsub("µg","mcg",names(USDAwide)))
#USDA database lacks this information
USDAwide[,Price:=NA_real_]
USDAwide[,Chromium_mcg:=NA_real_]
USDAwide[,Biotin_mcg:=NA_real_]
USDAwide[,Iodine_mcg:=NA_real_]

purl("Nutrient Research.Rmd")
purl("MyFoods.Rmd")
source("Nutrient Research.r")
source("MyFoods.r")



#define ease of use functions
findNutrientName <- function(x) {names(blank.food)[grepl(x,tolower(names(blank.food)))]}
findFoodName <- function(x) {
  USDAwide[grepl(tolower(x),tolower(Long_Desc)),]
}
```